Panel Seminars

### 2021-11-04 WGS_intro.Rmd
Changed format of site to Bootswatch

---
layout: default
title: Whole Genome Resequencing
parent: Choosing a PopGenomics Approach
grand_parent: Best Principles
has_children: true
#editor_options: 
#  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Choosing a PopGenomics Approach  
{: .no_toc }

<details open markdown="block">
  <summary>
    Table of contents
  </summary>
  {: .text-delta }
1. TOC
{:toc}
</details>

## Whole Genome Resequencing for Population Genomics  
For the purposes of this guide, we use "whole genome (re)sequencing (WGS)) to refer to  methods where a reference genome exists (whether for the focal species or a related species), and samples are sequenced and then mapped to most or all of the reference genome. This method can provide high density SNPs, structural information...for population genomic analyses. This is separate from whole-genome de novo sequencing, which aims to produce a reference genome by sequencing and assembling a complete genome for the first time.   
WGS can be divided into three main approaches, and choosing between these or RADseq(link to ) mostly depends on your questions of interest.   
1) high coverage individual WGS (hcWGS)  
+ description  
2) low coverage individual WGS (lcWGS)  
+ description
3) pooled individuals (Poolseq)  
RADseq is... and m

@@

### Tutorials

@@

## Considerations Before Lab Work

```{r, echo=FALSE,eval=FALSE}
library(knitr)
my.jekyll.site <- "marineomics.github.io"
KnitPost <- function(input, base.url = my.jekyll.site) {
  opts_knit$set(base.url = base.url)
  fig.path <- paste0("images/", sub(".Rmd$", "", basename(input)), "/")
  opts_chunk$set(fig.path = fig.path)
  opts_chunk$set(fig.cap = "center")
  render_jekyll()
  knit(input, envir = parent.frame())
}

setwd("~/Postdoc_Projects/RCN_MarineOmics/Website/marineomics.github.io/guidelines/")
KnitPost("~/Postdoc_Projects/RCN_MarineOmics/Website/marineomics.github.io/guidelines/WGS_intro.Rmd")

```

>>>>

---
bibliography: bibtexlib.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitcitations)
opts_chunk$set(fig.width = 10,
               fig.height = 5,
               cache = FALSE)
cite_options(citation_format = "pandoc", max.names = 3, style = "html", 
             hyperlink = "to.doc")
```

# Whole Genome Resequencing for Population Genomics  
For the purposes of this guide, we use "whole genome (re)sequencing (WGS)) to refer to  methods where a reference genome exists (whether for the focal species or a related species), and samples are sequenced and then mapped to most or all of the reference genome. This method can provide high density SNPs, structural information...for population genomic analyses. This is separate from whole-genome de novo sequencing, which aims to produce a reference genome by sequencing and assembling a complete genome for the first time.   
WGS can be divided into three main approaches, and choosing between these or RADseq(link to ) mostly depends on your questions of interest.   
1) high coverage individual WGS (hcWGS)  
+ description  
2) low coverage individual WGS (lcWGS)  
+ description
3) pooled individuals (Poolseq)  
RADseq is... and m

@@

## Tutorials

@@

# Considerations Before Lab Work

### 2021-11-04 index.Rmd
Changed format of site to Bootswatch

---
layout: default
title: "Panel Seminars"
nav_order: 1
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# About

The MarineOmics working group is part of the [RCN for Evolution in Changing Seas](https://rcn-ecs.github.io/), and was formed to promote reproducible and robust genomic research in marine science. Methods in next generation sequencing and bioinformatics advance at a pace that quickly render any static set of best practices as obsolete. To support robust 'omics research now and moving forward, the working group will disseminate guidelines through an easily-interfaced and dynamic website that will be deployed in August 2021. *Keep an eye on this URL for updates!*

# Panel Seminar Series

To facilitate discussions about practices and pitfalls in applying 'omics to non-model systems, we are hosting Q & A panel seminars with experts on topics ranging from RADseq, population genomics with WGS, and transcriptomics. Seminars are every two weeks, on **Fridays from 11:00-12:15 US Central Time**. 3-5 expert panelists will discuss each topic, with questions coming from the working group and the audience. If you would like to submit a question for the panelists ahead of time, please send an email to rcnecs.marineomics[at]gmail.com .

Everyone is welcome to join! All seminars will be recorded and available on this website.

**To receive a Zoom link, please fill out the registration form [here](
https://auburn.zoom.us/meeting/register/tZ0ode2rpz4sG9Il_TuYexWfqd6HyjdQ58Zi).**

## Seminar Schedule

| Date        | Topic       | Panelists     | Video     |
| :---        | :---        | :---          | :---      |
| May 7         | GBS/RADseq genotyping pipelines     | [Melanie LaCava](https://melanielacava.weebly.com/), [Alicia Mastretta-Yanes](http://mastrettayanes-lab.org/), [Isaac Overcast](https://isaacovercast.github.io/), [Jon Puritz](https://www.marineevoeco.com/)   | [View video](https://www.youtube.com/watch?v=C74GBESeIq4)     |
| May 21       |  WGS genotyping (low and high coverage)     | [Jeffrey Good](http://www.thegoodlab.org/), [Mikhail "Misha" Matz](https://matzlab.weebly.com/), [Noah Reid](http://nreid.github.io/), [Tim Sackton](https://scholar.harvard.edu/tsackton), [Nina Overgaard Therkildsen](https://www.therkildsenlab.com/) | [View Video](https://www.youtube.com/watch?v=ObJ3OT3dwSw)    |
| June 4       |  Population genomic analyses and filtering data     | [Zach Gompert](https://gompertlab.com/), [Morgan Kelly](http://www.morgankelly.biology.lsu.edu/), [Katie Lotterhos](https://sites.google.com/site/katielotterhos/home), [Jeff Ross-Ibarra](https://rilab.ucdavis.edu/) |     |
| June 18       |  RNAseq (experimental design through differential expression)     | [Ana Conesa](http://conesalab.org/), [Sarah Davies](http://sites.bu.edu/davieslab/), [Martin Hölzer](https://hoelzer-lab.github.io/), [Joanna Kelley](https://labs.wsu.edu/genomes/), [Harold Pimentel](https://pimentellab.com/)     |     |

# Reproducibility in Marine Genomics  
The working group is also currently hosting three undergraduate research interns with funding from the [RCN-ECS](https://rcn-ecs.github.io/). These interns are part of a sub-committee conducting a literature survey to characterize trends in data availability, code accessibility, and methods reproducibility in papers that use genomics to study adaptation in marine systems. The results of this survey will be shared in a peer-reviewed article, along with guidance to improve the state of reproducibility in the field.

@@

#### [Katherine Silliman, PhD](https://ksilliman.weebly.com/), Auburn University - kes0132[at]auburn.edu
#### [Sam Bogan](http://www.hofmannlab.com/sam-bogan.html), UC-Santa Barbara -snbogan[at]ucsb.edu
#### [Alan Downey-Wall](https://cos.northeastern.edu/people/alan-downey-wall/), Northeastern University 
#### Chris Mantegna, University of Washington  
#### [Danielle Davenport](https://www.researchgate.net/profile/Danielle-Davenport-2), University of Queensland  
#### [Hanny Rivera, PhD](https://www2.whoi.edu/staff/hrivera/), Woods Hole Oceanographic Institute  
#### Jecy Klinkam, College of William and Mary  
#### [Joanna Griffiths, PhD](https://joannasgriffiths.wordpress.com/), UC-Davis
#### [Joe McGirr, PhD](https://joemcgirr.github.io/), UC-Davis 
#### Kaitlin Macaranas, CSU-Bakersfield 
#### Megan Guidry, University of Rhode Island
#### Natalie Ameral, University of Rhode Island & RI Dept. of Environmental Management  
#### Nicolas Lou, Cornell University
#### [Sara Schaal](https://schaals.wixsite.com/smschaal), Northeastern University 
#### [Sara Wuitchik, PhD](https://sjswuitchik.weebly.com/), Harvard University

### Faculty Advisors
#### [Andrew Whitehead, PhD](https://whiteheadresearch.wordpress.com/), UC-Davis 
#### [Jon Puritz, PhD](https://www.marineevoeco.com/), University of Rhode Island 
#### [Steven Roberts, PhD](http://faculty.washington.edu/sr320/?page_id=10850), University of Washington

@@

``````{r, echo=FALSE,eval=FALSE}
library(knitr)
my.jekyll.site <- "marineomics.github.io"
KnitPost <- function(input, base.url = my.jekyll.site) {
  opts_knit$set(base.url = base.url)
  fig.path <- paste0("images/", sub(".Rmd$", "", basename(input)), "/")
  opts_chunk$set(fig.path = fig.path)
  opts_chunk$set(fig.cap = "center")
  render_jekyll()
  knit(input, envir = parent.frame())
}

setwd("~/Postdoc_Projects/RCN_MarineOmics/Website/marineomics.github.io/")
KnitPost("~/Postdoc_Projects/RCN_MarineOmics/Website/marineomics.github.io/index.Rmd")

```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
---
title: "Introduction"
---

# BETA TEST OF SITE!

The MarineOmics working group is part of the [RCN for Evolution in Changing Seas](https://rcn-ecs.github.io/), and was formed to promote **reproducible** and **robust** genomic research in nonmodel species, but especially marine and aquatic studies. Methods in next generation sequencing and bioinformatics advance at a pace that quickly render any static set of best practices as obsolete. To support robust 'omics research now and moving forward, the working group helps disseminate guidelines through this dynamic, open-sourced website.

**Rigorous**:  following best principles to identify and mitigate sources of error in data generation and analysis

**Reproducible**: when others can reproduce the results with accessible data, code, and documentation

# Guidelines for 'omics analyses

On this website you will find a collection of guidelines, tutorials, recommended readings, and method evaluations for various 'omics analyses that are commonly used in studies of nonmodel systems (particularly marine species). Instead of providing rigid "best practices", we aim to encourage data exploration and rigorous quality control through "best practices".

Based on the expertise of the working group, we have developed content for these topics:

## Topics {.tabset .tabset-fade .tabset-pills}
### Population Genomics

* [Choosing a population genomics sequencing approach](WGS_intro.html)  
* [Whole Genome Resequencing](WGS_intro.html)  
* [Reduced Representation Sequencing](RADseq.html)

### Functional Genomics

* Transcriptomics with RNA-Seq (coming soon!)  
* Differential gene expression (coming soon!)

## {-}

## Panel Seminars 
To facilitate discussions about practices and pitfalls in applying 'omics to non-model systems, we hosted [Q & A panel seminars](panels.html) with experts on topics ranging from RADseq, population genomics with WGS, and transcriptomics. Check them out on [YouTube](https://www.youtube.com/channel/UCosG6JfIj7k0DizfsD5ADfQ)!

# Reproducibility in Marine Genomics  
The working group is also interested in evaluating and improving reproducibility in studies that use genomics to study adaptation in marine systems. utilizing genomics in marine species, through a peer-reviewed literature survey of data availability, code accessibility, and methods reproducibility. In Spring 2021, three undergraduate research interns contributed to this literature survey, with funding from the [RCN-ECS](https://rcn-ecs.github.io/).

@@

#### [Katherine Silliman, PhD](https://ksilliman.weebly.com/), Auburn University - kes0132[at]auburn.edu {.unlisted .unnumbered}
#### [Sam Bogan](http://www.hofmannlab.com/sam-bogan.html), UC-Santa Barbara -snbogan[at]ucsb.edu {.unlisted .unnumbered}
#### [Alan Downey-Wall](https://cos.northeastern.edu/people/alan-downey-wall/), Northeastern University {.unlisted .unnumbered}
#### Chris Mantegna, University of Washington  {.unlisted .unnumbered}
#### [Danielle Davenport](https://www.researchgate.net/profile/Danielle-Davenport-2), University of Queensland {.unlisted .unnumbered}  
#### [Hanny Rivera, PhD](https://www2.whoi.edu/staff/hrivera/), Woods Hole Oceanographic Institute  {.unlisted .unnumbered}
#### Jecy Klinkam, College of William and Mary  {.unlisted .unnumbered}
#### [Joanna Griffiths, PhD](https://joannasgriffiths.wordpress.com/), UC-Davis {.unlisted .unnumbered}
#### [Joe McGirr, PhD](https://joemcgirr.github.io/), UC-Davis {.unlisted .unnumbered}
#### Kaitlin Macaranas, CSU-Bakersfield {.unlisted .unnumbered}
#### Megan Guidry, University of Rhode Island {.unlisted .unnumbered}
#### Natalie Ameral, University of Rhode Island & RI Dept. of Environmental Management {.unlisted .unnumbered}  
#### Nicolas Lou, Cornell University {.unlisted .unnumbered}
#### [Sara Schaal](https://schaals.wixsite.com/smschaal), Northeastern University {.unlisted .unnumbered} 
#### [Sara Wuitchik, PhD](https://sjswuitchik.weebly.com/), Harvard University {.unlisted .unnumbered}

### Faculty Advisors {.unlisted .unnumbered}
#### [Andrew Whitehead, PhD](https://whiteheadresearch.wordpress.com/), UC-Davis {.unlisted .unnumbered}
#### [Jon Puritz, PhD](https://www.marineevoeco.com/), University of Rhode Island {.unlisted .unnumbered}
#### [Steven Roberts, PhD](http://faculty.washington.edu/sr320/?page_id=10850), University of Washington {.unlisted .unnumbered}

@@
